Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-07-17 workflow/workflow.Rmd
Small changes

```{r setNormAssay}
assays(dataObj)<-assays(dataObj)[c("normalizedValues","residuals","counts")]
```

@@

plotHeatmap(dataObj, 
            whichClusters = c("makeConsensus","publishedClusters"), clusterFeaturesData = "all",
            clusterSamplesData = "dendrogramValue", breaks = 0.99,
            sampleData = c("Batch", "Experiment"),
            clusterLegend = metaColors, annLegend = FALSE, main = "")
```

>>>>

```{r setNormAssay}
assays(dataObj)<-assays(dataObj)[c("normalizedValues","residuals","counts","weights")]
```

@@

plotHeatmap(dataObj, 
            whichClusters = c("makeConsensus","publishedClusters"), clusterFeaturesData = "all",
            clusterSamplesData = "dendrogramValue", breaks = 0.99,
            colData = c("Batch", "Experiment"),
            clusterLegend = metaColors, annLegend = FALSE, main = "")
```
